Verifying Demonstrations

### 2018-03-19 paper/protocol.tex
Minor clarifications, \hat -> \tilde

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(k, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^k 
  Z^r\) and send \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol: \(\PK[k,r][M = g^k Z^r]\).
If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (\sigma, k, r)\).

@@

\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness simply should simply get a time-correlated random value from the 
time-stamping service, \(t_s'\gets \TSget\).
(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
start of the time interval of creation for the proof share.).

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\gets \ZZ_q^*\) and let \(
  \hat\sigma = (\hat A = A^{r_1},
                \hat B = B^{r_1},
                \hat Z_B = Z_B^{r_1},
                \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\hat\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \hat\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \hat A &\neq 1 \\
  e(g, \hat B) &= e(Y, \hat A) \\
  e(g, \hat Z_B) &= e(Z, \hat B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \hat A) \\
  v_{xy} &= e(X, \hat B) \\
  v_{xy}' &= e(X, \hat Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}

>>>>

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(k, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^k 
  Z^r\) and send \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (\sigma, k, r)\).

@@

\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the 
time-stamping service, \(t_s'\gets \TSget\).
(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
start of the time interval of creation for the proof share.).

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\gets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(pid\).)
The participant sends \((pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    pid = g_T^{1/(k+cid)} \right\}.
\end{multline*}
